outline!

### 2016-05-23 paper.tex
paper: update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\subsection{Optimzer}

@@

Here we show the derivation of two other interfaces that are in production in
Ceph today to demonstrate the generality of our interface.

@@

Include performance management topic in related work.

%In this section we examine the design space for implementing the CORFU
%protocol in the RADOS storage system. Table \ref{t:init-ds} shows the entire
%design space. A description of each design parameter follows:
%
%{\bf Mapping strategy.} The method by which a log entry---identified by its
%logical position---is addressed within RADOS is referred to as the mapping
%strategy. A 1:1 strategy stores each log entry in a RADOS object with a
%distinct name (e.g. ``mylog.pos443''), and an N:1 strategy stripes the log
%positions across a set of objects (e.g.  round-robin). While we do consider
%both strategies in this paper, a 1:1 strategy is attractive because it allows
%a design in which clients can directly address log positions by constructing
%the correct object name.
%
%{\bf Storage interface.} entry data may be small or large. its primary
%storage location is important. kv, bs. we further sub-divide bs into
%write and append. each strategy is compatible with fixed size entries
%except for the write interface.
%
%{\bf Logical addressing.}

%\subsection{Storage Interface Selection}
%
%Figure \ref{f:librados-sweep} shows the single-node write-only I/O throughput
%for each of the points in the design space defined in Table \ref{t:init-ds}.
%The results reveal poor relative performance using both the key-value storage
%interface, as well as either of the 1:1 strategies---which incur overhead by
%creating a new object for each log entry. Both of the N:1 strategies using the
%bytestream I/O interface outperform all of the other approaches by over 2x
%throughput, but otherwise have nearly identical performance.
%
%To examine the read performance of the points in the design space we generated
%a dataset using each of the write workloads, and then issued random reads
%across the entire dataset. Figure \ref{f:librados-rand-read} shows the read
%throughput for each of the design strategies. The results show that an N:1
%mapping using bytestream interface performs best. Interestingly, the 1:1
%mapping strategy using the bytestream interface exhibits good read performance
%in comparison to writes using the same strategy.

%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\textwidth]{experiments/librados-sweep/output.soft.reset.2hr.png}
%  \caption{
%[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/librados-sweep/visualize.ipynb}{source}]
%Throughput (IOPS) of 1K writes to a single OSD using the standard I/O
%interfaces in various configurations. The best performance is achieved using
%the byte stream interface and a N:1 mapping strategy.
%}
%\end{figure}
%
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\textwidth]{experiments/basic-cls-rand-read/output.read.60min.png}
%  \caption{
%[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/basic-cls-rand-read/visualize.ipynb}{source}]
%Throughput of 1K random reads to a single OSD using the standard I/O
%interfaces in various configurations. The best performance is achieved using
%the byte stream interface and a N:1 mapping strategy.
%}
%\end{figure}
%
%\begin{figure}[h]
%  \centering
%  \includegraphics[width=0.45\textwidth]{experiments/basic-cls-overhead/output.1024.soft.reset.png}
%  \caption{
%[\href{https://github.com/noahdesu/zlog-popper/tree/master/experiments/basic-cls-overhead/visualize.ipynb}{source}]
%}
%\end{figure}

%As a first approximation these results show that when optimizing for log
%append and random read throughput the design space should be refined by
%limiting solutions to architectures based on a N:1 mapping strategy using the
%bytestream I/O interface. But what these microbenchmarks explicitly omit are
%the overheads associated with metadata management such as enforcing write-once
%semantics or using an index to map a log position to a physical offset within
%an object. In the next section we

>>>>

\subsection{Optimizer}

@@

The subset of the Bloom language we are using is powerful enough to express the
CORFU language, as well as many of the object class interfaces that are already
included in Ceph. We briefly sketch the Bloom imlementation of an object class
that provides a locking service. This is an interesting example because Bloom
implementations use mechanisms for introducing points of coordination in
execution, which in the context of Ceph, may be written in Bloom itself.

\begin{lstlisting}[caption={Hello}, label=lab]
bloom :take_lock do
end

bloom :break_lock do
end

bloom :list_locks do
end

bloom :lock_info do
end
\end{lstlisting}

@@

Include performance management topic in future work.
